This chapter elaborates on the power budget and requirements leading to the proposed solar array design. Reference Sols and their rover modes are defined in \refSec{sec:Design:ReferenceSols} so that mission scenario power budgets may be formalized in \refSec{sec:Design:PowerBudget}. Particular attention is put on analyzing field trial data from which propulsion power draw requirements are extracted. \refSec{sec:Design:RequirementsAndDesignDrivers} consolidates assumptions, requirements, conwtraints, and design drivers that will guide the proposed design of the rover's \ac{PV} system. Solar array sizing and configurations as well as necessary rover body redesign are presented in \refSec{sec:Design:SolarArray}. A rudimentary simulation environment for solar power management is introduced in \refSec{sec:Design:Simulation} as a potential for future work before summarizing and concluding the chapter in \refSec{sec:Design:SummaryAndConclusion}.

\section{Reference Sols}
\label{sec:Design:ReferenceSols}
\input{sections/design/reference-sols/index.tex}

\clearpage
\section{Power Budget}
\label{sec:Design:PowerBudget}
\input{sections/design/power-budget/index.tex}

\clearpage
\section{Requirements and Design Drivers}
\label{sec:Design:RequirementsAndDesignDrivers}
\input{sections/design/requirements-and-design-drivers/index.tex}

\clearpage
\section{Solar Array}
\label{sec:Design:SolarArray}
\input{sections/design/solar-array/index.tex}

\section{Simulation}
\label{sec:Design:Simulation}
\input{sections/design/simulation/index.tex}

\section{Summary and Conclusion}
\label{sec:Design:SummaryAndConclusion}
This chapter defined reference Sols and their power budgets from which \ac{SA} design requirements and constraints were fine tuned. Two \ac{SA} designs were proposed, one for each mission site. Their conceptualization was driven by maximizing traverse gains obtained from leveraging the rover's suspension system as a \ac{SA} orientation and inclination mechanism. The results obtained from simple simulations were described which showcased the advantages in solar power output that the proposed inclined driven design offers when compared to a traditional horizontal surface configuration. The simulated data was produced by a custom built \ac{PMS} implemented for as part of this thesis.
