The thesis is structured in five chapters. The foundation of the thesis are presented in the two chapters following the introduction. Power subsystems of past, ongoing, and planned missions are briefly introduced in Chapter \ref{sec:StateOfTheArt}. The \ac{SOA} of solar and battery cell technologies built on top of mission heritage are then summarized. Chapter \ref{sec:MarsSolarEnergy} rigorously explores the Martian solar radiation environment from which two mission sites are selected. These serves as the primary driver in defining worst case scenarios that will impose environmental design constraints.

The design of the proposed \ac{PV} power system is described in Chapter \ref{sec:PowerSystemDesign}. Reference Sols and their power budgets are formalized in order to fine tune feasable requirements and design drivers. Two distinct \ac{SA} designs are presented for each mission site and a brief simulation prototype is introduced. The thesis is concluded in Chapter \ref{sec:ConclusionAndOutlook} which also provides an outlook for future research and developments.

Additional material is provided in Appendices. Verification of the mars solar insolation R package developed for this thesis is presented in Appendix \ref{sec:Appendix:InsolationCalculationVerification}. The solar energy predictions calculated by the R package was also validate against \ac{MER} ground truth data. An attempt to reduce the observed divergences is elaborated in Appendix \ref{sec:Appendix:EnergyErrorMargin}. Finally, background information regarding optimal \ac{SA} inclination and orientation angles are found in Appendix \ref{sec:Appendix:OptimalAngles}.
