Baseline content for this section is taken from \citeother{CDF2014} and constrained to the scope of this thesis. Adjustements are made in relation to the mission sites described in the previous chapter as well as with the rover's capabilities with respect to its active suspension system. Rover modes are identified and then sequenced into high-level reference Sols. Defining rover modes and reference Sols serve as a prerequisite to formalizing power budgets by assignment each rover modes with their power draw and operational duration.

%The chapter is structured as follows: Section \ref{sec:ReferenceSols:RoverModes} provides general definitions of rover modes. The identified rover modes are sequenced into reference Sols in Section \ref{sec:ReferenceSols:ReferenceSols}. The chapter is then summarized in Section \ref{sec:PowerBudget:SummaryAndConclusion}.

\subsection{Rover Modes}
\label{sec:ReferenceSols:RoverModes}
Not all modes defined in \citeother{CDF2014} are included in this section, however; they may become of interest in future design iterations. The omitted modes are \textit{Launch}, \textit{\ac{EDL}}, \textit{Deployment}, \textit{Science Stop - Long},  and \textit{Safe} modes. The rover modes considered in this thesis are:

\begin{enumerate}[label=\textcolor{BulletBlue}{(\alph*)}]
    \item \textbf{Traverse - Flat:} Pre-planned flat surface traverses to target destinations.
    \item \textbf{Traverse - Upslope:} Pre-planned upslope surface traverses to target destinations.
    \item \textbf{Science Stop - Short:} Short science activities in between traverses.
    \item \textbf{\ac{DTE} Communication:} Pre-planned communication sessions.
    \item \textbf{Idle - Day:} All day dedicated to charging batteries.
    \item \textbf{Idle - Night:} Minimal battery usage during night.
    \item \textbf{Hibernation:} Survival mode during dust storms.
    \item \textbf{Optimal Pose:} Repositioning the rover along its principal yaw, pitch, and roll axes to maximized next Sol \ac{SA} power generation.
\end{enumerate}
%\ac{DTE} Communication operations are encapsulated as their own mode whereas \ac{UHF} Communications are mode activities conducted during \textit{Traverse}, \textit{Science Stop}, and \textit{Idle} modes.

%Communication operations and their schedules were also taken from \citeother{CDF2014}:
%\begin{itemize}
%    \item Uplink of sol plan either early in the morning (\SI{30}{\minute} \ac{DTE} or \SI{7}{\minute} \ac{UHF}) or during the night (\SI{7}{\minute} \ac{UHF}).
%    \item Downlink of high priority data required for planning of the next sol either in the afternoon (\SI{5}{\minute} \ac{DTE}) or during the night (\SI{7}{\minute} \ac{UHF}).
%\end{itemize}

The \textit{Optimal Pose} mode is not taken from \citeother{CDF2014}. It is created for the purpose of this study so that the rover may use its active suspension system as a \ac{SA} orienting mechanism to maximize \ac{SA} power generation. The inclination angle resulting from a pith or roll rotations is  the $\beta$ angle. The orientation angle with respect to the direction of the equator is the surface azimuth angle $\gamma_{c}$ obtained from a yaw rotations. These angles are introduced in \refSec{sec:MartianEnvironment:SolarRadiation:InclinedSurface}. Rover subsystems as well as their states during the rover modes are taken from \citeother{CDF2014} and shown in \refTab{tab:rover-modes}.

 %Some mode durations were adjusted from those presented in \citeother{CDF2014} in response to power budgeting constraints pertaining to the scope of this research.

\input{sections/design/reference-sols/tables/rover-modes.tex}



\subsection{Reference Sols}
\label{sec:ReferenceSols:ReferenceSols}
Flat and upslope traverses are the worst-case modes in terms of energy requirements. Worst case hibernation scenarios are tied to battery charge and discharge rates during dust storms in which insufficient solar energy is generated. As such, the scope of this thesis only requires that \textit{Flat Traverse}, \textit{Upslope Traverse}, and \textit{Hibernation} be analyzed.


\subsubsection{Traverse Sol}
\label{sec:ReferenceSols:TraverseSol}
A \textit{Traverse Sol} allows the rover to reach a pre-planned target destination. Flat and upslope traverses have identical mode sequences, shown in \refTab{tab:mission-scenario-traverse-sol}, only differing in the duration of their respective \textit{Traverse} modes. This distinction relates to propulsion power draw differences that are presented in \refSec{sec:Design:PowerBudget}.

\input{sections/design/reference-sols/tables/mission-scenario-traverse-sol.tex}

A Traverse Sol begins with the \textit{Idle - Day mode}, which is mostly dedicated to recharging the rover's batteries. At the end of the previous Sol, the \ac{SA} was tilted and oriented into an optimal configuration with respect to the current Sol's sun path in order to maximize power generation. The \textit{\ac{DTE} Communication mode}  follows after which the received traversing commands are processed during the \textit{Traverse mode}. A short time slot is alotted to science operations during the \textit{Science Stop - Short mode} so that multiple traverse Sols do not result in lack of scientific return, particularly for long multi-Sol traverse campaigns. The rover then assumes an optimal power generation pose during the \textit{Optimal Pose mode} to ensure maximum \ac{SA} power generation on the next Sol. Finally, the \textit{Idle - Night mode} is engaged during which the rover's survival is ensured with heaters that thermally regulate all critical systems.

The mechanical feasibility of achieving $\beta_{opt}$ or $\beta_{best}$ does not imply operational feasibility with respect to other subsystems. For instance, pitching the rover may hinder communication \ac{LOS} or produce thermal imbalances that would complicate heating the rover's critical systems. The implications are a systems engineering problem that is beyond the scope of this study. The assumption is made that all rover subsystems are designed to functional nominally for $\beta_{opt}$ and $\beta_{best}$ given all possible $\gamma_{c}$.

%\subsection{Science Sol}
%\label{sec:ReferenceSols:ScienceSol}
%The Science Sol maximizes science data collection. The mode sequence is shown in Table \ref{tab:mission-scenario-science-sol}. It only differs from the Traverse Sol with a \textit{Science Stop - Long} mode instead of a \textit{Traverse} mode.
%\input{sections/design/reference-sols/tables/mission-scenario-science-sol.tex}

%\clearpage
%\subsection{Battery Recharge Sol}
%\label{sec:ReferenceSols:BatteryRechargeSol}
%The Battery Recharge Sol dedicates an entire Martian day to recharging the rover's batteries. The sequence and duration of its modes are shown in Table \ref{tab:mission-scenario-science-sol}. Only thermal and communication operations are executed during this Sol so that power draws from the battery are minimized in order to prioritize attaining the target charge state. No rover repositioning is required to adjust the \ac{SA} $\beta$ angle as it will have already been set to $\beta_{optimal}$ or $\beta_{best}$ at the end of a previous Sol.

%\input{sections/design/reference-sols/tables/mission-scenario-battery-recharge-sol.tex}

\subsubsection{Hibernation Sol}
\label{sec:ReferenceSols:HibernationSol}
The \textit{Hibernation Sol} is the rover's survival mode during a dust storm. In this setting, the rover solely draws power from its battery. Only the heaters and a timer are active so that energy may be conserved.

\input{sections/design/reference-sols/tables/mission-scenario-hibernation-sol.tex}

\subsection{Summary}
\label{sec:ReferenceSols:SummaryAndConclusion}
Rover modes are used to define reference Sols. Of particular interest is the \textit{Optimal Mode} mode which takes advantage of the rover's active suspension system to maximize power generation and battery charging during the \textit{Idle - Day mode}. Distinctions were made between two types of \textit{Traverse} modes with respect to flat or upslope terrain topography.

% Operation durations were established for each mode as a prerequesite to determining power budgets in the following chapter.
