This chapter elaborates on the power budget and requirements leading to the \ac{SA} design. Reference Sols and their rover modes are defined in \refSec{sec:Design:ReferenceSols} so that mission scenario power budgets may be formalized in \refSec{sec:Design:PowerBudget}. Propulsion power draw requirements are extracted from analyzing field trial data. \refSec{sec:Design:RequirementsAndDesignDrivers} consolidates assumptions, requirements, contraints, and design drivers that guide the \ac{PV} system design. \ac{SA} sizing and configurations as well as necessary rover body redesign are presented in \refSec{sec:Design:SolarArray}. A rudimentary simulation environment for solar power management is introduced in \refSec{sec:Design:Simulation} as a potential for future work before summarizing and concluding the chapter in \refSec{sec:Design:SummaryAndConclusion}.

\section{Reference Sols}
\label{sec:Design:ReferenceSols}
\input{sections/power-system-design/reference-sols/index.tex}

\clearpage
\section{Power Budget}
\label{sec:Design:PowerBudget}
\input{sections/power-system-design/power-budget/index.tex}

\clearpage
\section{Requirements and Design Drivers}
\label{sec:Design:RequirementsAndDesignDrivers}
\input{sections/power-system-design/requirements-and-design-drivers/index.tex}

\clearpage
\section{Solar Array}
\label{sec:Design:SolarArray}
\input{sections/power-system-design/solar-array/index.tex}

\clearpage
\section{Simulation}
\label{sec:Design:Simulation}
\input{sections/power-system-design/simulation/index.tex}

\section{Summary and Conclusion}
\label{sec:Design:SummaryAndConclusion}
This chapter defines reference Sols and their power budgets from which \ac{SA} design requirements and constraints are fine tuned. Two \ac{SA} designs are proposed, one for each mission site. Their conceptualization is driven by maximizing traverse gains obtained from leveraging the rover's suspension system as a \ac{SA} orientation and inclination mechanism. The results obtained from simulations are described which showcase the solar power output gains that an inclined driven design offers when compared to a horizontal configuration. The simulated data is produced by a custom built \ac{PMS} implemented as part of this thesis.
